---
title: "Campaign outcome prediction for Bank marketing"
output: html_document
author: 'Vishal Gupta & Vishu Agarwal'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```


```{r library, warning=FALSE, include=FALSE}
library(MCMCpack)
library(lme4)
library(caret)
library(MLmetrics)
library(knitr)
library(ggplot2)
```

## Goal

To build a model using current campaign, past campaign and customer information to predict whether a consumer is going to subscribe term deposit once the campaign is done. An initial description of the data is a below - 




```{r data_load}
train = read.csv('../data/train_transformed_ds.csv')
test = read.csv('../data/test_transformed.csv')
print(dim(train))
head(train)
```


Data contains raw features, with and without transformation, as well as one hot encoded variables to ensure no more transformation is required at any later stages. Cyclicity for day of the month and month of the year is created to ensure correct representation of the information.


## Modeling

Due to high number of variables in the dataset, first a few formulation will be tried out to set up the baseline and understand the importance of variable in prediction. Further improvements and adjustment can be based on the performance and outcome of each model. 

**Possible models**

*1. Baseline*

term_deposit_subscribed ~ job_type + marital + education + default + housing_loan + personal_loan + communication_type + prev_campaign_outcome + prev_campaign_contact + balance + last_contact_duration + num_contacts_in_campaign + num_contacts_prev_campaign + month + day_of_month + customer_age

*2. Transformed variables - balance indicator and log transformed*

term_deposit_subscribed ~ job_type + marital + education + default + housing_loan + personal_loan + communication_type + prev_campaign_outcome + prev_campaign_contact + balance_ind + log_balance + log_last_contact_duration + log_num_contacts_in_campaign + log_num_contacts_prev_campaign + month + day_of_month + customer_age

*3. Adding Cyclicity*

term_deposit_subscribed ~ job_type + marital + education + default + housing_loan + personal_loan + communication_type + prev_campaign_outcome + prev_campaign_contact + balance_ind + log_balance + log_last_contact_duration + log_num_contacts_in_campaign + log_num_contacts_prev_campaign + month_sin + month_cos + day_of_month_sin + day_of_month_cos + customer_age

*4. (i) Adding random effects - job_type*

term_deposit_subscribed ~ marital + education + default + housing_loan + personal_loan + communication_type + prev_campaign_outcome + prev_campaign_contact + balance_ind + log_balance + log_last_contact_duration + log_num_contacts_in_campaign + log_num_contacts_prev_campaign + month_sin + month_cos + day_of_month_sin + day_of_month_cos + customer_age | job_type

*4. (ii) Adding random effects - marital*

term_deposit_subscribed ~ job_type + education + default + housing_loan + personal_loan + communication_type + prev_campaign_outcome + prev_campaign_contact + balance_ind + log_balance + log_last_contact_duration + log_num_contacts_in_campaign + log_num_contacts_prev_campaign + month_sin + month_cos + day_of_month_sin + day_of_month_cos + customer_age | marital

*4. (iii) Adding random effects - education*

term_deposit_subscribed ~ job_type + marital + default + housing_loan + personal_loan + communication_type + prev_campaign_outcome + prev_campaign_contact + balance_ind + log_balance + log_last_contact_duration + log_num_contacts_in_campaign + log_num_contacts_prev_campaign + month_sin + month_cos + day_of_month_sin + day_of_month_cos + customer_age | education


**Evaluation Criteria**

We want to focus more on the customer who are more likely to create a term deposit after the campaign, as it can help identify the attributes in a customer that can make future campaigns more effective. Accuracy, for this purpose, might not be accuracy as we have a unbalanced classes case where most of the customer (>80%) dont subscribe the term deposit. *Recall (sensitivity or true positive rate) will be the primary metrics* as it evaluate the model on reducing false negative (where customer actually made a term deposit but model predicted otherwise). *Second metric of focus will be Precision*, that evaluates false positive for model performance, since they are very less customer that subscribe term deposit, predicting them as positive will not increase the campaign load significantly. Also, these can be the customers that have the potential to subscribe the term deposit in future campaigns. 

```{r performnce_df}
performance = data.frame(model=character(), recall=numeric(), precision=numeric())
```

**1. Baseline - logistic regression with raw inputs**

```{r model1}
base_lm = glm(term_deposit_subscribed ~ job_type + marital + education + default + housing_loan + personal_loan + communication_type + prev_campaign_outcome + prev_campaign_contact + balance + last_contact_duration + num_contacts_in_campaign + num_contacts_prev_campaign + month + day_of_month + customer_age, data=train, family=binomial(link='logit'))

summary(base_lm)

print('AIC values is ')
AIC(base_lm)

base_lm_train_pred = base_lm$fitted.values
base_lm_train_pred = as.numeric(base_lm_train_pred > 0.5)

# table(base_lm_train_pred, train$term_deposit_subscribed)
# print('Train confusion matrix as below - ')
# confusionMatrix(as.factor(base_lm_train_pred), as.factor(train$term_deposit_subscribed), positive = '1')

# for sensitivity and specificity
act = test$term_deposit_subscribed
pred = predict(base_lm, test)
pred = as.numeric(pred > 0.5)
test_set = data.frame(obs=as.factor(act), pred=as.factor(pred))

# table(base_lm_train_pred, train$term_deposit_subscribed)
print('Test confusion matrix as below - ')
cm = confusionMatrix(as.factor(pred), as.factor(act), positive = '1')
cm

model = 'Baseline LM'
rec = round(100*cm$byClass['Sensitivity'], 2)
pre = round(100*cm$byClass['Pos Pred Value'], 2)

performance = rbind(performance, c(model, rec, pre))
colnames(performance) = c('Model', 'Recall', 'Precision' )
# prSummary(test_set, lev = levels(test_set$obs))

# precision(as.factor(pred), as.factor(act))
# recall(as.factor(pred), as.factor(act))
```

**2. Transformed variables - balance indicator and log transformed**

```{r model2}
glm1 = glm(term_deposit_subscribed ~ job_type + marital + education + default + housing_loan + personal_loan + communication_type + prev_campaign_outcome + prev_campaign_contact + balance_ind_positive + log_balance + log_last_contact_duration + log_num_contacts_in_campaign + log_num_contacts_prev_campaign + month + day_of_month + customer_age, data=train, family=binomial(link='logit'))

summary(glm1)

print('AIC values is ')
AIC(glm1)

glm1_train_pred = glm1$fitted.values
glm1_train_pred = as.numeric(glm1_train_pred > 0.5)

# table(glm1_train_pred, train$term_deposit_subscribed)
# print('Train confusion matrix as below - ')
# confusionMatrix(as.factor(glm1_train_pred), as.factor(train$term_deposit_subscribed), positive = '1')

# for sensitivity and specificity
act = test$term_deposit_subscribed
pred = predict(glm1, test)
pred = as.numeric(pred > 0.5)
test_set = data.frame(obs=as.factor(act), pred=as.factor(pred))

# table(glm1_train_pred, train$term_deposit_subscribed)
print('Test confusion matrix as below - ')
cm = confusionMatrix(as.factor(pred), as.factor(act), positive = '1')
cm

model = 'LM - log balance and positive indication'
rec = round(100*cm$byClass['Sensitivity'], 2)
pre = round(100*cm$byClass['Pos Pred Value'], 2)
performance = rbind(performance, c(model, rec, pre))

# prSummary(test_set, lev = levels(test_set$obs), model = glm1)

# precision(as.factor(pred), as.factor(act))
# recall(as.factor(pred), as.factor(act))
```

**3. Adding Cyclicity - Month of the year and day of the month**

```{r model3}
glm2 = glm(term_deposit_subscribed ~ job_type + marital + education + default + housing_loan + personal_loan + communication_type + prev_campaign_outcome + prev_campaign_contact + balance_ind_positive + log_balance + log_last_contact_duration + log_num_contacts_in_campaign + log_num_contacts_prev_campaign + month_sin + month_cos + day_of_month_sin + day_of_month_cos + customer_age, data=train, family=binomial(link='logit'))

summary(glm2)

print('AIC values is ')
AIC(glm2)

glm2_train_pred = glm2$fitted.values
glm2_train_pred = as.numeric(glm2_train_pred > 0.5)

# table(glm2_train_pred, train$term_deposit_subscribed)
# print('Train confusion matrix as below - ')
# confusionMatrix(as.factor(glm2_train_pred), as.factor(train$term_deposit_subscribed), positive = '1')

# for sensitivity and specificity
act = test$term_deposit_subscribed
pred = predict(glm2, test)
pred = as.numeric(pred > 0.5)
test_set = data.frame(obs=as.factor(act), pred=as.factor(pred))

# table(glm2_train_pred, train$term_deposit_subscribed)
print('Test confusion matrix as below - ')
cm = confusionMatrix(as.factor(pred), as.factor(act), positive = '1')
cm

model = 'LM - added cyclicity'
rec = round(100*cm$byClass['Sensitivity'], 2)
pre = round(100*cm$byClass['Pos Pred Value'], 2)
performance = rbind(performance, c(model, rec, pre))

# prSummary(test_set, lev = levels(test_set$obs), model = glm2)

# precision(as.factor(pred), as.factor(act))
# recall(as.factor(pred), as.factor(act))
```


**4.1. Adding random effects - job_type**

```{r model4_1}
# glm3 = glmer(term_deposit_subscribed ~ education + housing_loan + personal_loan + communication_type + prev_campaign_outcome + balance_ind_positive + log_balance + log_last_contact_duration + log_num_contacts_in_campaign + month_sin + day_of_month_cos + log_num_contacts_prev_campaign + 1|job_type,
#              data=train, 
#              family=binomial(link='logit'),
#              glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=1000)))
glm3 = MCMChlogit(fixed=term_deposit_subscribed ~ marital + education + default + housing_loan + personal_loan + communication_type + 
                    prev_campaign_outcome + prev_campaign_contact + balance_ind_positive + log_balance + log_last_contact_duration + 
                    log_num_contacts_in_campaign + log_num_contacts_prev_campaign + month_sin + month_cos + day_of_month_sin + 
                    day_of_month_cos + customer_age, 
                    random=~1, group='job_type', data=train, mcmc=1000, r=2, R=diag(1))

summary(glm3$mcmc)

glm3_train_pred = glm3$theta.pred
glm3_train_pred = as.numeric(glm3_train_pred > 0.5)

# table(glm3_train_pred, train$term_deposit_subscribed)
# print('Train confusion matrix as below - ')
# confusionMatrix(as.factor(glm3_train_pred), as.factor(train$term_deposit_subscribed), positive = '1')

# for sensitivity and specificity
act = test$term_deposit_subscribed

# predicting using mcmc package

test$job_type_admin = as.numeric(test$job_type == 'admin')
x_test = rbind(1, test$marital_married, test$marital_single, test$marital_unknown,
               test$education_secondary, test$education_tertiary, test$education_unknown, 
               test$default_yes, test$housing_loan_yes, test$personal_loan_yes, test$communication_type_telephone, test$communication_type_unknown,
               test$prev_campaign_outcome_other, test$prev_campaign_outcome_success, test$prev_campaign_outcome_unknown, test$prev_campaign_contact_yes,
               test$balance_ind_positive, test$log_balance, test$log_last_contact_duration, test$log_num_contacts_in_campaign, test$log_num_contacts_prev_campaign,
               test$month_sin, test$month_cos, test$day_of_month_sin, test$day_of_month_cos, test$customer_age,
               test$job_type_admin, test$job_type_blue.collar, test$job_type_entrepreneur, test$job_type_housemaid,
               test$job_type_management, test$job_type_retired, test$job_type_self.employed, test$job_type_services, 
               test$job_type_student, test$job_type_technician, test$job_type_unemployed, test$job_type_unknown)

print(c(dim(x_test)[1], dim(glm3$mcmc)[2]-3))

glm3_coef = apply(glm3$mcmc, c(2), mean)[1:dim(x_test)]
pred = 1/(1 + exp(-glm3_coef %*% x_test))

pred = as.numeric(pred > 0.5)
test_set = data.frame(obs=as.factor(pred), pred=as.factor(act))

# table(glm3_train_pred, train$term_deposit_subscribed)
print('Test confusion matrix as below - ')
cm = confusionMatrix(as.factor(pred), as.factor(act), positive = '1')
cm

model = 'random effect - Job Type'
rec = round(100*cm$byClass['Sensitivity'], 2)
pre = round(100*cm$byClass['Pos Pred Value'], 2)
performance = rbind(performance, c(model, rec, pre))

# prSummary(test_set, lev = levels(test_set$obs), model = glm3)

# precision(as.factor(pred), as.factor(act))
# recall(as.factor(pred), as.factor(act))
```

**4.2. Adding random effects - marital**

```{r model4_2}
glm4 = MCMChlogit(fixed=term_deposit_subscribed ~ job_type + education + default + housing_loan + personal_loan + communication_type + 
                    prev_campaign_outcome + prev_campaign_contact + balance_ind_positive + log_balance + log_last_contact_duration + 
                    log_num_contacts_in_campaign + log_num_contacts_prev_campaign + month_sin + month_cos + day_of_month_sin + 
                    day_of_month_cos + customer_age, 
                    random=~1, group='marital', data=train, mcmc=1000, r=2, R=diag(1))

summary(glm4$mcmc)

glm4_train_pred = glm4$theta.pred
glm4_train_pred = as.numeric(glm4_train_pred > 0.5)

# table(glm4_train_pred, train$term_deposit_subscribed)
# print('Train confusion matrix as below - ')
# confusionMatrix(as.factor(glm4_train_pred), as.factor(train$term_deposit_subscribed), positive = '1')

# for sensitivity and specificity
act = test$term_deposit_subscribed

# predicting using mcmc package
test$marital_divorced = as.numeric(test$marital == 'divorced')
x_test = rbind(1, test$job_type_blue.collar, test$job_type_entrepreneur, test$job_type_housemaid,
               test$job_type_management, test$job_type_retired, test$job_type_self.employed, test$job_type_services, 
               test$job_type_student, test$job_type_technician, test$job_type_unemployed, test$job_type_unknown,
               test$education_secondary, test$education_tertiary, test$education_unknown, test$default_yes,
               test$housing_loan_yes, test$personal_loan_yes, test$communication_type_telephone, test$communication_type_unknown,
               test$prev_campaign_outcome_other, test$prev_campaign_outcome_success, 
               test$prev_campaign_outcome_unknown, test$prev_campaign_contact_yes,  test$balance_ind_positive, test$log_balance, test$log_last_contact_duration, test$log_num_contacts_in_campaign, test$log_num_contacts_prev_campaign, test$month_sin, test$month_cos,
               test$day_of_month_sin, test$day_of_month_cos, test$customer_age, 
               test$marital_divorced, test$marital_married, test$marital_single, test$marital_unknown
               )
print(c(dim(x_test)[1], dim(glm3$mcmc)[2]-3))

glm4_coef = apply(glm4$mcmc, c(2), mean)[1:dim(x_test)]
pred = 1/(1 + exp(-glm4_coef %*% x_test))


pred = as.numeric(pred > 0.5)
test_set = data.frame(obs=as.factor(pred), pred=as.factor(act))

# table(glm4_train_pred, train$term_deposit_subscribed)
print('Test confusion matrix as below - ')
cm = confusionMatrix(as.factor(pred), as.factor(act), positive = '1')
cm

model = 'random effect - Marital'
rec = round(100*cm$byClass['Sensitivity'], 2)
pre = round(100*cm$byClass['Pos Pred Value'], 2)
performance = rbind(performance, c(model, rec, pre))

# prSummary(test_set, lev = levels(test_set$obs), model = glm4)

# precision(as.factor(pred), as.factor(act))
# recall(as.factor(pred), as.factor(act))
```




**4.3. Adding random effects - education**

```{r model4_3}
glm5 = MCMChlogit(fixed=term_deposit_subscribed ~ job_type + marital + default + housing_loan + personal_loan + communication_type + 
                    prev_campaign_outcome + prev_campaign_contact + balance_ind_positive + log_balance + log_last_contact_duration + 
                    log_num_contacts_in_campaign + log_num_contacts_prev_campaign + month_sin + month_cos + day_of_month_sin + 
                    day_of_month_cos + customer_age, 
                    random=~1, group='education', data=train, mcmc=1000, r=2, R=diag(1))

summary(glm5$mcmc)

glm5_train_pred = glm5$theta.pred
glm5_train_pred = as.numeric(glm5_train_pred > 0.5)

# table(glm5_train_pred, train$term_deposit_subscribed)
# print('Train confusion matrix as below - ')
# confusionMatrix(as.factor(glm5_train_pred), as.factor(train$term_deposit_subscribed), positive = '1')

# for sensitivity and specificity
act = test$term_deposit_subscribed

# predicting using mcmc package
test$education_primary = as.numeric(test$education == 'primary')
x_test = rbind(1, test$job_type_blue.collar, test$job_type_entrepreneur, test$job_type_housemaid,
               test$job_type_management, test$job_type_retired, test$job_type_self.employed, test$job_type_services, 
               test$job_type_student, test$job_type_technician, test$job_type_unemployed, test$job_type_unknown,
               test$marital_married, test$marital_single, test$marital_unknown, test$default_yes,
               test$housing_loan_yes, test$personal_loan_yes, test$communication_type_telephone, test$communication_type_unknown,
               test$prev_campaign_outcome_other, test$prev_campaign_outcome_success, 
               test$prev_campaign_outcome_unknown, test$prev_campaign_contact_yes,  test$balance_ind_positive, test$log_balance, test$log_last_contact_duration, test$log_num_contacts_in_campaign, test$log_num_contacts_prev_campaign, test$month_sin, test$month_cos,
               test$day_of_month_sin, test$day_of_month_cos, test$customer_age,
               test$education_primary, test$education_secondary, test$education_tertiary, test$education_unknown
               )
print(c(dim(x_test)[1], dim(glm3$mcmc)[2]-3))

glm5_coef = apply(glm5$mcmc, c(2), mean)[1:dim(x_test)]
pred = 1/(1 + exp(-glm5_coef %*% x_test))


pred = as.numeric(pred > 0.5)
test_set = data.frame(obs=as.factor(pred), pred=as.factor(act))

# table(glm5_train_pred, train$term_deposit_subscribed)
print('Test confusion matrix as below - ')
cm = confusionMatrix(as.factor(pred), as.factor(act), positive = '1')
cm

model = 'Random effect - Education'
rec = round(100*cm$byClass['Sensitivity'], 2)
pre = round(100*cm$byClass['Pos Pred Value'], 2)
performance = rbind(performance, c(model, rec, pre))

# prSummary(test_set, lev = levels(test_set$obs), model = glm5)

# precision(as.factor(pred), as.factor(act))
# recall(as.factor(pred), as.factor(act))
```

```{r first_iter_output}
kable(performance, caption='Performace of different models after first modeling iteration')
```


### Model improvement


<!-- **Adding multiple random effects** -->

<!-- Job Type, Marital status and Education level, all these three random effects have improved performance significantly, hence we will try a model formulation having all three random effects. Since  -->

*Multiple random effects*
Based on the performance we can note that job type as hierarchical group has performed a lot better, hence it will be used along with education and marital status as random effect.

*Interaction*
Possible interaction terms - 
1. Log balance with balance indicator - this will make the model assume zero balance and truncate the distribution for negative values
2. Previous contact flag with number of contacts in previous campaign
3. Balance can have different impact on probability of term deposit subscription hence it can be used as random effect

*Variable selection*
Based on significant variable in linear models we can try using statistically significant variables


**Enhancement - Marital and education random effects with job type group**

```{r model5_1}
glm_i1 = MCMChlogit(fixed=term_deposit_subscribed ~ default + housing_loan + personal_loan + communication_type + 
                    prev_campaign_outcome + prev_campaign_contact + balance_ind_positive + log_balance + log_last_contact_duration + 
                    log_num_contacts_in_campaign + log_num_contacts_prev_campaign + month_sin + month_cos + day_of_month_sin + 
                    day_of_month_cos + customer_age, 
                    random=~1+marital+education, group='job_type', data=train, mcmc=1000, r=8, R=diag(7))

summary(glm_i1$mcmc)

# predicting using mcmc package
x_test = rbind(1, test$default_yes,
               test$housing_loan_yes, test$personal_loan_yes, test$communication_type_telephone, test$communication_type_unknown,
               test$prev_campaign_outcome_other, test$prev_campaign_outcome_success, 
               test$prev_campaign_outcome_unknown, test$prev_campaign_contact_yes,  test$balance_ind_positive, test$log_balance, test$log_last_contact_duration, test$log_num_contacts_in_campaign, test$log_num_contacts_prev_campaign, test$month_sin, test$month_cos,
               test$day_of_month_sin, test$day_of_month_cos, test$customer_age,
               test$job_type_admin, test$job_type_blue.collar, test$job_type_entrepreneur, test$job_type_housemaid,
               test$job_type_management, test$job_type_retired, test$job_type_self.employed, test$job_type_services, 
               test$job_type_student, test$job_type_technician, test$job_type_unemployed, test$job_type_unknown,
               test$marital_married*test$job_type_admin , 	test$marital_married*test$job_type_blue.collar , 	test$marital_married*test$job_type_entrepreneur , 	test$marital_married*test$job_type_housemaid , 	test$marital_married*test$job_type_management , 	test$marital_married*test$job_type_retired , 	test$marital_married*test$job_type_self.employed , 	test$marital_married*test$job_type_services , 	test$marital_married*test$job_type_student , 	test$marital_married*test$job_type_technician , 	test$marital_married*test$job_type_unemployed , 	test$marital_married*test$job_type_unknown , 	test$marital_single*test$job_type_admin , 	test$marital_single*test$job_type_blue.collar , 	test$marital_single*test$job_type_entrepreneur , 	test$marital_single*test$job_type_housemaid , 	test$marital_single*test$job_type_management , 	test$marital_single*test$job_type_retired , 	test$marital_single*test$job_type_self.employed , 	test$marital_single*test$job_type_services , 	test$marital_single*test$job_type_student , 	test$marital_single*test$job_type_technician , 	test$marital_single*test$job_type_unemployed , 	test$marital_single*test$job_type_unknown , 	test$marital_unknown*test$job_type_admin , 	test$marital_unknown*test$job_type_blue.collar , 	test$marital_unknown*test$job_type_entrepreneur , 	test$marital_unknown*test$job_type_housemaid , 	test$marital_unknown*test$job_type_management , 	test$marital_unknown*test$job_type_retired , 	test$marital_unknown*test$job_type_self.employed , 	test$marital_unknown*test$job_type_services , 	test$marital_unknown*test$job_type_student , 	test$marital_unknown*test$job_type_technician , 	test$marital_unknown*test$job_type_unemployed , 	test$marital_unknown*test$job_type_unknown , 	test$education_secondary*test$job_type_admin , 	test$education_secondary*test$job_type_blue.collar , 	test$education_secondary*test$job_type_entrepreneur , 	test$education_secondary*test$job_type_housemaid , 	test$education_secondary*test$job_type_management , 	test$education_secondary*test$job_type_retired , 	test$education_secondary*test$job_type_self.employed , 	test$education_secondary*test$job_type_services , 	test$education_secondary*test$job_type_student , 	test$education_secondary*test$job_type_technician , 	test$education_secondary*test$job_type_unemployed , 	test$education_secondary*test$job_type_unknown , 	test$education_tertiary*test$job_type_admin , 	test$education_tertiary*test$job_type_blue.collar , 	test$education_tertiary*test$job_type_entrepreneur , 	test$education_tertiary*test$job_type_housemaid , 	test$education_tertiary*test$job_type_management , 	test$education_tertiary*test$job_type_retired , 	test$education_tertiary*test$job_type_self.employed , 	test$education_tertiary*test$job_type_services , 	test$education_tertiary*test$job_type_student , 	test$education_tertiary*test$job_type_technician , 	test$education_tertiary*test$job_type_unemployed , 	test$education_tertiary*test$job_type_unknown , 	test$education_unknown*test$job_type_admin , 	test$education_unknown*test$job_type_blue.collar , 	test$education_unknown*test$job_type_entrepreneur , 	test$education_unknown*test$job_type_housemaid , 	test$education_unknown*test$job_type_management , 	test$education_unknown*test$job_type_retired , 	test$education_unknown*test$job_type_self.employed , 	test$education_unknown*test$job_type_services , 	test$education_unknown*test$job_type_student , 	test$education_unknown*test$job_type_technician , 	test$education_unknown*test$job_type_unemployed , 	test$education_unknown*test$job_type_unknown 
               )
# print(c(dim(x_test)[1], dim(glm_i1$mcmc)[2]-3))

glm_i1_coef = apply(glm_i1$mcmc, c(2), mean)[1:dim(x_test)]
pred = 1/(1 + exp(-glm_i1_coef %*% x_test))


pred = as.numeric(pred > 0.5)
test_set = data.frame(obs=as.factor(pred), pred=as.factor(act))

# table(glm_i1_train_pred, train$term_deposit_subscribed)
print('Test confusion matrix as below - ')
cm = confusionMatrix(as.factor(pred), as.factor(act), positive = '1')
cm

model = 'Random effect - Marital + Education | Job type'
rec = round(100*cm$byClass['Sensitivity'], 2)
pre = round(100*cm$byClass['Pos Pred Value'], 2)
performance = rbind(performance, c(model, rec, pre))


```

Performance has decreased by adding more complexity to the model, as the dataset is the same but number of parameters have increased drastically.

**Enhancement - Job type group with variable selection and interaction terms**

```{r model5_2}
glm_i2 = MCMChlogit(fixed=term_deposit_subscribed ~  housing_loan + personal_loan + communication_type + 
                    prev_campaign_outcome + prev_campaign_contact_yes:log_num_contacts_prev_campaign  + balance_ind_positive:log_balance +
                    log_num_contacts_in_campaign + log_last_contact_duration + month_sin + 
                    day_of_month_cos, 
                    random=~1+marital+education, group='job_type', data=train, mcmc=1000, r=8, R=diag(7))

summary(glm_i2$mcmc)

# predicting using mcmc package
x_test = rbind(1,
               test$housing_loan_yes, test$personal_loan_yes, 
               test$communication_type_telephone, test$communication_type_unknown, 
               test$prev_campaign_outcome_other, test$prev_campaign_outcome_success, test$prev_campaign_outcome_unknown, 
               test$log_num_contacts_in_campaign,
               test$log_last_contact_duration,
               test$month_sin, test$day_of_month_cos,
               
               test$prev_campaign_contact_yes*test$log_num_contacts_prev_campaign,  
               test$balance_ind_positive*test$log_balance, test$log_last_contact_duration, 
               
               test$job_type_admin, test$job_type_blue.collar, test$job_type_entrepreneur, test$job_type_housemaid,
               test$job_type_management, test$job_type_retired, test$job_type_self.employed, test$job_type_services, 
               test$job_type_student, test$job_type_technician, test$job_type_unemployed, test$job_type_unknown,
               test$marital_married*test$job_type_admin , 	test$marital_married*test$job_type_blue.collar , 	test$marital_married*test$job_type_entrepreneur , 	test$marital_married*test$job_type_housemaid , 	test$marital_married*test$job_type_management , 	test$marital_married*test$job_type_retired , 	test$marital_married*test$job_type_self.employed , 	test$marital_married*test$job_type_services , 	test$marital_married*test$job_type_student , 	test$marital_married*test$job_type_technician , 	test$marital_married*test$job_type_unemployed , 	test$marital_married*test$job_type_unknown , 	test$marital_single*test$job_type_admin , 	test$marital_single*test$job_type_blue.collar , 	test$marital_single*test$job_type_entrepreneur , 	test$marital_single*test$job_type_housemaid , 	test$marital_single*test$job_type_management , 	test$marital_single*test$job_type_retired , 	test$marital_single*test$job_type_self.employed , 	test$marital_single*test$job_type_services , 	test$marital_single*test$job_type_student , 	test$marital_single*test$job_type_technician , 	test$marital_single*test$job_type_unemployed , 	test$marital_single*test$job_type_unknown , 	test$marital_unknown*test$job_type_admin , 	test$marital_unknown*test$job_type_blue.collar , 	test$marital_unknown*test$job_type_entrepreneur , 	test$marital_unknown*test$job_type_housemaid , 	test$marital_unknown*test$job_type_management , 	test$marital_unknown*test$job_type_retired , 	test$marital_unknown*test$job_type_self.employed , 	test$marital_unknown*test$job_type_services , 	test$marital_unknown*test$job_type_student , 	test$marital_unknown*test$job_type_technician , 	test$marital_unknown*test$job_type_unemployed , 	test$marital_unknown*test$job_type_unknown , 	test$education_secondary*test$job_type_admin , 	test$education_secondary*test$job_type_blue.collar , 	test$education_secondary*test$job_type_entrepreneur , 	test$education_secondary*test$job_type_housemaid , 	test$education_secondary*test$job_type_management , 	test$education_secondary*test$job_type_retired , 	test$education_secondary*test$job_type_self.employed , 	test$education_secondary*test$job_type_services , 	test$education_secondary*test$job_type_student , 	test$education_secondary*test$job_type_technician , 	test$education_secondary*test$job_type_unemployed , 	test$education_secondary*test$job_type_unknown , 	test$education_tertiary*test$job_type_admin , 	test$education_tertiary*test$job_type_blue.collar , 	test$education_tertiary*test$job_type_entrepreneur , 	test$education_tertiary*test$job_type_housemaid , 	test$education_tertiary*test$job_type_management , 	test$education_tertiary*test$job_type_retired , 	test$education_tertiary*test$job_type_self.employed , 	test$education_tertiary*test$job_type_services , 	test$education_tertiary*test$job_type_student , 	test$education_tertiary*test$job_type_technician , 	test$education_tertiary*test$job_type_unemployed , 	test$education_tertiary*test$job_type_unknown , 	test$education_unknown*test$job_type_admin , 	test$education_unknown*test$job_type_blue.collar , 	test$education_unknown*test$job_type_entrepreneur , 	test$education_unknown*test$job_type_housemaid , 	test$education_unknown*test$job_type_management , 	test$education_unknown*test$job_type_retired , 	test$education_unknown*test$job_type_self.employed , 	test$education_unknown*test$job_type_services , 	test$education_unknown*test$job_type_student , 	test$education_unknown*test$job_type_technician , 	test$education_unknown*test$job_type_unemployed , 	test$education_unknown*test$job_type_unknown 
               )
# print(c(dim(x_test)[1], dim(glm_i2$mcmc)[2]-3))

glm_i2_coef = apply(glm_i2$mcmc, c(2), mean)[1:dim(x_test)]
pred = 1/(1 + exp(-glm_i2_coef %*% x_test))


pred = as.numeric(pred > 0.5)
test_set = data.frame(obs=as.factor(pred), pred=as.factor(act))

# table(glm_i2_train_pred, train$term_deposit_subscribed)
print('Test confusion matrix as below - ')
cm = confusionMatrix(as.factor(pred), as.factor(act), positive = '1')
cm

model = 'Random effect - Variable selection & Interactions'
rec = round(100*cm$byClass['Sensitivity'], 2)
pre = round(100*cm$byClass['Pos Pred Value'], 2)
performance = rbind(performance, c(model, rec, pre))


```


### Final Results & Impact

Recall & Precision for all the models are as below - 

```{r final_performance}
kable(performance, caption='Performace of all models')

customer_base_redn = round(100*sum(cm$table[1, ])/sum(cm$table), 1)
customer_miss = round(100*sum(cm$table[1, 2])/sum(cm$table[, 2]), 1)

print(c(customer_miss, customer_base_redn))
```

As we can observe, the final improvements with variables selection, adding interaction terms of customer balance & previous campaign contact with random effects is performing the best with 98.3% recall. The probability distribution curve of different classes can be seen as below

Based on the analysis we can reduce the customer base by `r customer_base_redn`% though loosing on only `r customer_miss`% customer who would have subscribed to term deposit


```{r class_prob_distribution, warning=FALSE}
glm_i2_coef = apply(glm_i2$mcmc, c(2), mean)[1:dim(x_test)]
pred = 1/(1 + exp(-glm_i2_coef %*% x_test))

test_set = data.frame(act=as.vector(pred), pred=as.vector(act))

ggplot(test_set, aes(x = act)) + 
  geom_histogram(binwidth = .05) + 
  facet_wrap(~pred) + 
  xlab("Probability of Class #1")

```

